Colonies - Compute Continuums across Platforms

### 2023-04-02 paper_2023/paper.tex
wip

\begin{equation}
    \label{eq:pt}
    priority_{time}=priority \cdot -10^9 \cdot 60 \cdot 60 \cdot 24 + submission_{time}  
\end{equation}

Implementing queue functionality using a database can be achieved in SQL by utilizing the \emph{order by timestamp} and \emph{limit 1} clauses to select tasks according to their submission times. Upon submission of a task, a \emph{priority time} value is computed and stored in the database. The primary objective of the priority time is to modify the submission timestamp by subtracting a delta time calculated as a function a priority value. This enables prioritization of more critical tasks. Equation \ref{eq:pt} shows how the priority time is calculated.

@@

Figure \ref{fig:process_assignment} illustrates an executor submitting a function specification that is later assigned to another executor. When registering, executors have to specify to the Colonies server which functions they are capable of executing. The Colonies server makes sure that the conditions (i.e requirmenets) of a function specification matches the capability of an executor. 
\begin{figure}[h]
	\centering
    \includegraphics[scale=0.35]{function_spec.png}
	\caption{Example of a function spec.}
	\label{fig:function_spec}
\end{figure}

>>>>

\begin{equation}
    \label{eq:pt}
    priority_{time}=submission_{time} - priority \cdot 10^9 \cdot 60 \cdot 60 \cdot 24
\end{equation}

Implementing queue functionality using a database can be achieved in SQL by utilizing the \emph{order by timestamp} and \emph{limit 1} clauses to select tasks according to their submission times. Upon submission of a task, a \emph{priority time} value is computed and stored in the database. The primary objective of the priority time is to modify the submission timestamp by subtracting a delta time calculated as a function a priority value. This enables prioritization of more critical tasks. Equation \ref{eq:pt} shows how the priority time is calculated for a nanosecond timestamp.

@@

Figure \ref{fig:process_assignment} illustrates an executor submitting a function specification that is later assigned to another executor. When registering, executors have to specify to the Colonies server which functions they are capable of executing. The Colonies server makes sure that the conditions (i.e requirmenets) of a function specification matches the capability of an executor. Note that the executors are responsibility of interpreting the assigned process and function specification to execute relevant code.

\begin{figure}[h]
	\centering
    \includegraphics[scale=0.35]{function_spec.png}
	\caption{Example of a function spec.}
	\label{fig:function_spec}
\end{figure}
